Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
make more room

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface. Tor users in censored environments and some of our participants
    will be required to select the correct bridge for circumventing censorship.
    Note that the interface prompts users to choose a transport type, which can be
    the source of confusion. Bridges are non-listed guard relays to the Tor
    network, and some of them can have transport types which obfuscate traffic in
    different ways.}
\end{figure}

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
of Tor to date, measuring how users configure Tor in three different adversarial settings. 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, we will be designing ways to improve the interface to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
to design a mock-up interface for an alternative configuration interface which will
greatly automate the process. There are tradeoffs between ease of use and transparency
of the systems, and ethical considerations with loggable errors resulting from automated configuration. 
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}

>>>>

\begin{figure}[t]
\label{fig:bridges}
  \centering
    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
    \caption{The Tor Bridges Configuration window of the Tor configuration
    interface. Tor users in censored environments and some of our participants
    will be required to select the correct bridge for circumventing censorship.
    Note that the interface prompts users to choose a transport type, which can be
    the source of confusion. Bridges are non-listed guard relays to the Tor
    network; transports, supported by bridges, obfuscate traffic in
    different ways.}
\end{figure}

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Test the Tor configuration interface} We will perform the largest user study 
of Tor, measuring Tor configuration in three different adversarial settings. 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, we will be design and test improvements to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
to design a mock-up interface for an alternative configuration interface which will
greatly automate the process. There are tradeoffs between ease of use and transparency
of the systems, and ethical considerations with loggable errors resulting from automated configuration. 
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}
